---
title: "Dashboard_ASSET_Survey"
author: "Titouan Filloux"
date: "`r Sys.Date()`"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny
---

```{r global, include=FALSE}
pacman::p_load(
  rio,             # data import/export     
  here,            # locate files
  tidyverse,       # data management and visualization
  flexdashboard,   # dashboard versions of R Markdown reports
  shiny,           # interactive figures
  plotly,           # interactive figures
  dplyr
)
# import the linelist
All <- import("Newdata_TF.rds")
CropDesc <- import("CropDesc_TF.rds")
Cropsys <- import("Cropsys_TF.rds")
AnimalDesc <- import("AnimalDesc_TF.rds")
RnV <- readRDS("RnV_TF.rds")
Cropsyssum <- import("Cropsyssum.rds")
#Required changes
All$SW_Weight <- as.character(All$SW_Weight)
All$SW_Weight <- as.numeric(All$SW_Weight)
```

# Introduction

**Dashboard ASSET project survey - Cambodia, Laos, Vietnam - 2023/2024**

The aim of this dashboard is to present data collected among rural households in Cambodia, Laos and Vietnam as part of the ASSET project, during the first semester of 2023.\
\
To navigate in the different parts of the dashboard, use the **drop-down menus above** to display information for crops or cropping systems, then use the **drop-down menus on the left** of the board to select the study areas, crops, cropping systems...

# Information {.sidebar}

```{r}
library(flexdashboard)
library(dplyr)

#Drop-down menu of study area chosen
selectInput("Sarea_choice", label = "Select a study area to display:",
            choices = unique(CropDesc$Sarea), selected = unique(CropDesc$Sarea)[[1]])

area.choices = reactive({
 CropDesc %>%
  filter(Sarea==input$Sarea_choice)%>%
  mutate(Crop = as.character(Crop)) %>%
  arrange(Crop) %>% 
  mutate(Crop = as.factor(Crop))
})

#Drop-down menu for Crop choice
renderUI({selectInput("Crop_choice", label = "For Crops part - Select a crop to display:",
        choices = area.choices()$Crop, selected = area.choices()$Crop[[1]])})

area.choicesb = reactive({
  Cropsys %>%
  filter(Sarea==input$Sarea_choice & Crop==input$Crop_choice ) %>%
    arrange(Cropsys)
  Cropsys %>%
  filter(Sarea==input$Sarea_choice & Crop==input$Crop_choice)%>%
  mutate(Cropsys = as.character(Cropsys)) %>%
  arrange(Cropsys) %>% 
  mutate(Cropsys = as.factor(Cropsys))
})

#We create the Crop system choice drop-down menu
renderUI({selectInput("Cropsys_choice", label = "For Cropping systems part - Select a cropping system to display:",
            choices = area.choicesb()$Cropsys, selected = area.choicesb()$Cropsys[[1]])})



area.choicesc = reactive({
 AnimalDesc %>%
  filter(S_Area==input$Sarea_choice)%>%
  mutate(specie = as.character(specie)) %>%
  arrange(specie) %>% 
  mutate(specie = as.factor(specie))
})

#We create the Crop system choice drop-down menu
renderUI({selectInput("Animal_choice", label = "For Raising part - Select an animal specie to display:",
            choices = area.choicesc()$specie, selected = area.choicesc()$specie[[1]])})



```

<span style="color:red; font-style:italic">Definitions:\
- N Study area = Number of households in the study area (calculated based on sampling weights, stratification at village level)\
- N Crop / N Animal = Number of households growing a specific crop / raising a specific animal specie in the study area\
- N Cropsys = Number of households having a specific cropping system\
</span>

<span style="color:green; font-style:italic">Other information:\
- The % presented outside the tables are relative to the value 100 and the % presented in the tables are relative to the value 1.\
- "NA" can correspond to the non-existence of this information for the crop/animal-country combination or null values\
- Percentages that add up to less than 100 generally indicate missing information or information that is not taken into account because its value is too low\
- The number "2" at the end of a crop is not to be taken into account, e.g. "Cassava2"

# Cultivation {data-navmenu="Crops"}

## Row 1 {data-height=200}

### **General**

N Study area = **`r renderText({round(sum(All$SW_Weight[All$S_Area == input$Sarea_choice]), digits = 0)})`** / N Crop = **`r renderText({round(CropDesc$N[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice], digits = 0)})`**\
**`r renderText({CropDesc$PerCentofHouseholds[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]*100})`%** of households grow this crop (% of N Study area) \
Average area = **`r renderText({round(CropDesc$'Area - m2'[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]/10000, digits = 3)})` ha**\
Number of species grown: **`r renderText({round(CropDesc$NumberSpecies[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice], digits = 2)})`**\
**`r renderText({CropDesc$'-Conservation of traditionnal, local seeds'[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]*100})`%** of households are conserving/using local seeds (% of N Crop)

### **Sowing**

The unit most commonly used to quantify this crop "seeding" is:\
**`r renderText({CropDesc$MSeedUnit[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]})`** (**`r renderText({CropDesc$PerCentMSeedUnit[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]*100})`**% of N Crop)

```{r}
renderTable({
SowingT <- CropDesc[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice,c(8:12)]
SowingT <- SowingT %>%
  select_if(~ !any(is.na(.))) %>%
  add_column("Sowing Unit" = "Amount/ha") %>%
  select('Sowing Unit', everything())
print(SowingT)
})
```


## Row 2 {data-height= 800}

### **Main practices & AE practices implemented (>10% of N Crop)**

```{r}
renderTable({
AEP <- as.data.frame(t(CropDesc[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice,c(37:95)]))
colnames(AEP) <- "PerCent"
AEP = dplyr::filter(AEP, as.numeric(PerCent) >= 0.1)
AEP <- AEP %>% add_column("Category and practice" = rownames(AEP), .before = "PerCent")
print(AEP)
})
```

### **Area distribution**
```{r}
renderPlotly({
   columns_to_select <- ifelse(input$Sarea_choice == "Lao",     "district_eng_preload","commune_eng_preload")
  xlab <- ifelse(input$Sarea_choice == "Lao", "District","Commune")
  pattern <- paste0("d2_132.",input$Crop_choice)
  Area <- All %>% 
    filter(S_Area == input$Sarea_choice) %>%
      select(all_of(columns_to_select), starts_with(pattern))
  ggplotly(
    ggplot(Area, aes(x = Area[,1], y = Area[,2], fill = Area[,1])) + 
    geom_boxplot() + 
    ggtitle(paste(input$Sarea_choice," - ",input$Crop_choice,"\n Area (m2) - N = ", round(CropDesc$N[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice], digits = 0)))+
    theme(legend.position='none', plot.title = element_text(size = 12))+
    ylab("Area (m2)")+
    xlab(xlab)+
    scale_fill_viridis_d()
  )
})
```

# Production {data-navmenu="Crops"}

## Row 1 {data-height= 400}

### **Production and selling**
**`r renderText({CropDesc$PerCentSellers[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]*100})`%** of households (% of N crop) are selling **`r renderText({input$Crop_choice})`** (Form = **`r renderText({CropDesc$MFormWhenSold[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]})`** - **`r renderText({CropDesc$PerCentMFormWhenSold[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]})`**)
```{r}
renderTable({
  Prod <- as.data.frame(t(CropDesc[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice,c(13,20:21,23:24)]))
  colnames(Prod) <- "Average"
  Prod <- Prod %>% add_column("Production & selling" = rownames(Prod), .before = "Average")
print(Prod)
})
```

### **Reasons for growing this crop**
Main reason for growing this crop (% of N Crop):\
\
Household consumption preference: **`r renderText({CropDesc$"Reason% - Household consumption preferences"[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]*100})`**%\
Market price and demand: **`r renderText({CropDesc$"Reason% - Market price and demand"[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]*100})`**%\
Well adapted to local conditions: **`r renderText({CropDesc$"Reason% - Well adapted to local conditions"[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]*100})`**%



## Row 2 {data-height=600}

### **Yield distribution**
```{r}
renderPlotly({
   columns_to_select <- ifelse(input$Sarea_choice == "Lao",     "district_eng_preload","commune_eng_preload")
  xlab <- ifelse(input$Sarea_choice == "Lao", "District","Commune")
  pattern <- paste0("d2_ha135.",input$Crop_choice)
  Area <- All %>% 
    filter(S_Area == input$Sarea_choice) %>%
      select(all_of(columns_to_select), starts_with(pattern))
  ggplotly(
    ggplot(Area, aes(x = Area[,1], y = Area[,2], fill = Area[,1])) + 
    geom_boxplot() + 
    ggtitle(paste(input$Sarea_choice," - ",input$Crop_choice,"\n Yield (kg/ha) - N = ", round(CropDesc$N[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice], digits = 0)))+
    theme(legend.position='none', plot.title = element_text(size = 12))+
    ylab("Yield (kg/ha)")+
    xlab(xlab)+
    scale_fill_viridis_d()
  )
})
```

### **Gross product/ha distribution**
```{r}
renderPlotly({
   columns_to_select <- ifelse(input$Sarea_choice == "Lao",     "district_eng_preload","commune_eng_preload")
  xlab <- ifelse(input$Sarea_choice == "Lao", "District","Commune")
  pattern <- paste0("GrossProductha.",input$Crop_choice)
  Area <- All %>% 
    filter(S_Area == input$Sarea_choice) %>%
      select(all_of(columns_to_select), starts_with(pattern))
  if(!all(is.na(Area[,2]))) {
  ggplotly(
    ggplot(Area, aes(x = Area[,1], y = Area[,2], fill = Area[,1])) + 
    geom_boxplot() + 
    ggtitle(paste(input$Sarea_choice," - ",input$Crop_choice,"\n Gross product ($/ha) - N = ", round(CropDesc$N[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice], digits = 0)))+
    theme(legend.position='none', plot.title = element_text(size = 12))+
    ylab("Gross product ($/ha)")+
    xlab(xlab)+
    scale_fill_viridis_d()
  )
  } else {}
})
```


# Cropping constraints {data-navmenu="Crops" data-orientation=columns}

## Column 1 {data-width=400}

### **Main constraints faced by households (>10% of N Crop)**
```{r}
renderTable({
Cons <- as.data.frame(t(CropDesc[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice,c(28:36)]))
colnames(Cons) <- "PerCent"
Cons = dplyr::filter(Cons, as.numeric(PerCent) >= 0.1)
Cons <- Cons %>% add_column("Main constraints" = rownames(Cons), .before = "PerCent")
print(Cons)
})
```

### **Perception of cultivation requirements**
**`r renderText({CropDesc$"Obs-Crops requiring more water than others"[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]*100})`**% of households indicated that this Crops required more water than others\
**`r renderText({CropDesc$"Obs-Crops requiring heavy fertilization to thrive"[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]*100})`**% indicated it was requiring heavy fertilization to thrive\
**`r renderText({CropDesc$"Obs-Crops requiring heavy use of pesticides to thrive"[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice]*100})`**% indicated it was requiring heavy use of pesticides to thrive


## Column 2 {data-width=600}

### Constraints distribution
```{r}
renderPlotly({
    columns_to_select <- ifelse(input$Sarea_choice == "Lao",     "district_eng_preload","commune_eng_preload")
    pattern <- paste0("d81_b - Constraint.",input$Crop_choice)
    xlab <- ifelse(input$Sarea_choice == "Lao", "District","Commune")
    Beta <- All %>%
     filter(S_Area == input$Sarea_choice, !is.na(!!sym(pattern))) %>%
      select(all_of(columns_to_select), starts_with(pattern)) %>%
       group_by(!!sym(columns_to_select)) %>%
         count(!!sym(pattern)) %>% 
           mutate(prop = round(n / sum(n), digits = 2))
    Beta <- as.data.frame(Beta)
  ggplotly(    
  plotb <- ggplot(Beta, aes(x = Beta[,1], y = Beta[,4], fill = Beta[,2], label = Beta[,4]))+
    geom_col(colour="black",position = 'stack')+
    geom_text(size = 3, position = position_stack(vjust = 0.5))+
   ggtitle(paste(input$Sarea_choice," - ",input$Crop_choice,"\n Constraints - N = ", round(CropDesc$N[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice], digits = 0)))+
    theme(axis.text.x = element_text(size=9, angle = 85), legend.title = element_blank(), plot.title = element_text(size = 12))+
    ylab("Gross product ($/ha)")+
    xlab(xlab)+
    scale_fill_viridis_d())
})
```


# Overview {data-navmenu="Cropping systems"}
```{r}
output$image <- renderImage({
  switch(input$Sarea_choice,
         "Cambodia" = list(src = "CropSysOverview_Camb.jpg", width = "75%"),
         "Lao" = list(src = "CropSysOverview_Laos.jpg", width = "95%"),
         "Son La province" = list(src = "CropSysOverview_SL.jpg", width = "100%"),
         "Dien Bien province" = list(src = "CropSysOverview_DB.jpg", width = "100%"))
}, deleteFile = FALSE)

imageOutput("image")
```

# Description {data-navmenu="Cropping systems"}
**"Information" part is based on data collected during the surveys whild "Assumptions" part is made up of
interpretations made by cross-referencing this data with general knowledge of agriculture in the area (assumptions are unverified).**
```{r}
reactive({
if (input$Sarea_choice == "Cambodia") {  
if (input$Cropsys_choice == "Broadcasted rice - household consumption") {
cat("Information:\n
Very common cropping system (half of the sample), grown because of household consumption preferences\n
1-2ha of broadcasted rice, 71% of farmers build terraces, 60% use animal manure,
42% do land-leveling and 39% leave crop residues maintained to cover the soil\n
Average sowing amount (around 80-100 kg/ha), average yield (mostly <2 t/ha)\n
No selling. Many households (almost 50%) think it requires important amount of fertilizer/pesticides\n
\n
Assumptions:\n
- Crop grown for household consumption (150-200kg/hmember/year), no possibility of selling as not enough lands\n
- Use of pesticides (herbicides)\n
- Few fertilizers used out of animal manure")
} else if(input$Cropsys_choice == "Broadcasted rice - consumption and selling") {
  cat("Information:\n
Very common cropping system (One third of the sample)\n
Grown because of household consumption preferences and selling of additionnal production\n
2-3ha of broadcasted rice, 72% of farmers build terraces, 65% use animal manure,
48% do land-leveling and 38% leave crop residues maintained to cover the soil\n
Average sowing amount (around 80-100 kg/ha), average yield (mostly <2 t/ha)\n
No selling. Many households (almost 50%) think it require important amount of fertilizer\n
\n
Assumptions:\n
- Crop grown for household consumption (150-200kg/hmember/year)\n
- As enough land, selling of rice surplus\n
- Use of pesticides (herbicides)\n
- Few fertilizers used out of animal manure\n")
} else if(input$Cropsys_choice == "Broadcasted/transplanted rice with off-season vegetables") {
  cat("Information:\n
Uncommon cropping system (1% of the sample)\n
Area of rice and vegetables/peanut in the lowland, rice is not sold (motivated by household consumption preferences)\n
Most other crops are sold (Peanut, Savoy cabbage, Long bean, Cucumber,
Water spinach, Mustard greens, Pak Choy, Amaranth)\n
Some Melon and Savoy cabbage are not sold\n
On average 1ha of broadcasted rice, 72% of farmers build terraces, 66% use animal manure\n
51% do land-leveling and 44% leave crop residues maintained to cover the soil\n
Average sowing amount (around 70-80 kg/ha), average yield (mostly <2 t/ha)\n
For further information about vegetables production, check the following parts\n
\n
Assumptions:\n
- Rice grown for household consumption (150-200kg/hmember/year)\n
- Vegetables grown on a share of rice plots during the same year for commercial purposes\n
- Use of pesticides (herbicides) for broadcasted rice systems\n
- Few inputs for vegetables except possible fertilization for peanuts and water spinach")
} else if(input$Cropsys_choice == "Cassava monocropping") {
  cat("Information:\n
Common cropping system (45% of the sample)\n
Cassava monocropping in the upland, All the production is sold (Motivated by Market price and demand mostly)\n
On average 1.7ha of Cassava, 44% of farmers are weeding through mowing/slashing\n
Low density (around 2500 stems/ha = 2-meter horizontal and vertical spacing at ha ),\n
Average/low yield (In all villages except Rik Reay, mostly <5 t/ha, higher in Rik Reay)\n
35.6% indicated it was requiring heavy fertilization to thrive,
55.6% indicated it was requiring heavy use of pesticides to thrive
\n
Assumptions:\n
- Cassava grown as cash crop with low density and low input use due to low soil potential/low investment capacity\n
- Use of herbicides/mechanical weeding for households who are not using mowing/slashing\n
- Use of fertilizers as no other practice used to maintain soil fertility\n
- Possible that this crop is used in rotation with other upland crops (soybean, upland rice...)
but the information was missed during the interview")
} else if(input$Cropsys_choice == "Cashew - Plantations with annual crops intercropping") {
cat("Information:\n
Common cropping system (24% of the sample)\n
Cashew plantation in the upland with intercropping of cassava, soybean or upland rice\n
All the production is sold for productive plantation which represent half of the
farmers concerned by this cropping system (Motivated by Market price and demand mostly)\n
On average 1.9ha of Cassava, 38% of farmers are weeding through mowing/slashing and 33% are 
using weaver ants to protect cashew trees against pests\n
Normal/high density, around 200-300 trees/ha, Low yields (144 kg/ha/year)\n
28.8% indicated it was requiring heavy fertilization to thrive /
53.4% indicated it was requiring heavy use of pesticides to thrive\n
For associated annual crops, charcteristics are similar to their respectivecropping systems as pure crops
except lower sowing density (Cassava = 2000 stems/ha, Soybean = 50 kg of seeds/ha, Upland rice = 70 kg of seed/ha)
\n
Assumptions:\n
- Plots of young cashew plantation with no or low production, with annual crops in spacing with low densities and 
low input use due to low soil potential/low investment capacity and cashew trees presence in the plot\n
- Use of herbicides/mechanical weeding for households who are not using mowing/slashing, use of fertilizers 
as no other practice used to maintain soil fertility")
} else if(input$Cropsys_choice == "Soybean monocropping") {
  cat("Medium-common cropping system (15% of the sample)\n
Soybean monocropping in the upland, Almost all the production is sold (Motivated by Market price and demand mostly)\n
On average 1.2ha of Soybean, 40% of farmers are weeding through mowing/slashing\n
Medium-low density: around 50-60 kg/ha, average/low yield (In all villages except Rous Ran, mostly around 1 t/ha,
higher in Rous Ran)\n
53.9% indicated it was requiring heavy use of pesticides to thrive
\n
Assumptions:\n
- Soybean grown as cash crop with low density and low input use due to low soil potential/low investment capacity\n
- Use of herbicides/mechanical weeding for households who are not using mowing/slashing\n
- Use of fertilizers as no other practice used to maintain soil fertility\n
- Possible that this crop is used in rotation with other upland crops (cassava, upland rice...)
but the information was missed during the interview")
} else if(input$Cropsys_choice == "Fruit trees - Household consumption") {
cat("One farmer only, small plot of Guava (320 m2) with production probably used for household consumption 
(Household consumption preference). Probably very common in the area but this kind of cropping system was recorded
in the homegarden part which was not included in this dashboard")
} else if(input$Cropsys_choice == "Fruit trees - Productive plantations") {
cat("Uncommon cropping system (1.5% of the sample)\n
Fruit trees (Longan,Guava, Sweetsop, Lime, Bananas) in the upland, Almost all the production is sold 
except bananas sold and used for household consumption\n
Motivated by Market price and demand mostly\n
On average 0.5ha of Misc. fruit trees, Most farmers are using/practicing:
- Water ponds, swales digging
- Crop residues to cover the soil
- Fertilization through animal manure, Recycling crop waste & Ramial Wood Chip (RWC) or other wood chips
- Weeding through mowing/slashing
(100% for longan & guava, 50% for lime, 33% for sweetsop, only mowing slashing for bananas)\n
Variable density and low production:
- 100 trees/ha for longan - 200 kg/ha
- 2000 trees/ha for guava - 1.6 t/ha
- 200-350 trees/ha for sweetsop - Variable around 1.2 t/ha
- Variable for lime and bananas - Variable around 200 kg/ha for lime and 3250 kg/ha for bananas\n
For most kind of fruits: Insects constraint, requiring water, heavy fertilization and pesticides\n
Except for lime (no constraint and only requiring water) and Bananas (variable)
\n
Assumptions:\n
- Fruit trees grown as cash crop by households with possibility to do so (knowledge, land, labor force,
value chain access...)
with low to high density depending on the species, with many practices associated related to watering,
soil fertility and pest and disease management")
} else if(input$Cropsys_choice == "None") {
  cat("No cropping system related to this crop")
} else if(input$Cropsys_choice == "Cashew - Productive plantations") {
  cat("Information:\n
Common cropping system (51% of the sample)\n
Cashew plantation in the upland with no intercropping\n
All the production is sold (Motivated by Market price and demand mostly)\n
On average 2.2ha of Cashew, 54% of farmers are weeding through mowing/slashing and 62% are using 
weaver ants to protect cashew trees against pests\n
Normal density, around 200 trees/ha, Low yields (375 kg/ha/year)\n
23.3% indicated it was requiring heavy fertilization to thrive\
56.9% indicated it was requiring heavy use of pesticides to thrive\n
\n
Assumptions:\n
- Plots of mature cashew plantation with low production, potentially because still young (less than 5 years)\n or because low soil fertility potential and management\n
- Cashew = Cash crop for households")
} else if(input$Cropsys_choice == "Cashew - Young plantations") {
  cat("Information:\n
Common cropping system (6.1% of the sample)\n
Non-productive cashew plantation in the upland with no intercropping - Motivated by Market price and demand mostly\n
On average 1.5ha of Cashew, 51% of farmers are weeding through mowing/slashing and 59% are using weaver ants to
protect cashew trees against pests\n
Normal density, around 200-300 trees/ha\n
21.6% indicated it was requiring heavy fertilization to thrive /
45.9% indicated it was requiring heavy use of pesticides to thrive
\n
Assumptions:\n
- Plots of young non-productive cashew plantation with purpose to be cash crop for households, crop chosen because
well adapted to local condition\n
- Density seems to increase comparedd to mature plantation, which may indicate increasing investment by households 
in the aim of higher production.")
} else if(input$Cropsys_choice == "Upland rice monocropping") {
  cat("Uncommon cropping system (8.5% of the sample)\n
Upland rice monocropping in the upland,
Almost all the production is self-consumed (23% of households concerned are selling it)\n
Household consumption preference: 63.5%\n
On average 1.1ha of Upland rice, 38% of farmers are weeding through mowing/slashing, 38% are using land levelling
and 27% are using Animal manure\n
Medium-low density: around 60-80 kg/ha, average/low yield (In all villages except Reaksmei, mostly around 1.5 t/ha,
higher in Reaksmei)\n
92.3% of households indicated that this Crops required more water than others
21.2% indicated it was requiring heavy fertilization to thrive
42.3% indicated it was requiring heavy use of pesticides to thrive\n
\n
Assumptions:\n
- Upland rice grown as subsistence crop with low input use due to low soil potential/low investment capacity\n
- Some households with larger lands are able to produce enough to sell a part of their production\n
- Use of herbicides/mechanical weeding for households who are not using mowing/slashing\n
- More common to use animal manure here compared to other upland crops\n
- Possible that this crop is used in rotation with other upland crops (cassava, upland rice...)
but the information was missed during the interview")
} else if(input$Cropsys_choice == "Transplanted rice - household consumption") {
  cat("Information:\n
Medium-common cropping system (13% of households in this area), grown because of household consumption preferences\n
0.5-1.5ha of transplanted rice, 66% of farmers build terraces, 72% use animal manure\n
51% do land-leveling, 47% leave crop residues maintained to cover the soil and
46% are mowing/slashing\n
Low sowing amount (around 50-60 kg/ha), average yield (1.5-2.5 t/ha)\n
No selling. Many households (almost 50%) think it requires important amount of fertilizer
but lower for pesticides (around 20%)\n
\n
Assumptions:\n
- Crop grown for household consumption first (150-200kg/hmember/year), no possibility of selling as not much land\n
- Less seeds used and probably less use of herbicide than transplanted\n
- Few fertilizers used out of animal manure")
} else if(input$Cropsys_choice == "Transplanted rice - consumption and selling"){
  cat("Information:\n
Uncommon cropping system (8% of households in this area), grown because of household consumption preferences\n
1-2ha of transplanted rice, 74% of farmers build terraces, 80% use animal manure,
41% do land-leveling, 39% leave crop residues maintained to cover the soil and
55% are mowing/slashing\n
Low sowing amount (around 50-60 kg/ha), higher yield compared to this area (1.5-3.5 t/ha)\n
Selling on average half of the harvest. Many households (43%) think it requires important amount of fertilizer 
but lower for pesticides (around 20%)\n
\n
Assumptions:\n
- Crop grown for household consumption first (150-200kg/hmember/year), larger land means possibility of sellings\n
- Most productive local rice systems but probably more labor intensive\n
- Less seeds used and probably less use of herbicide than transplanted\n
- Few fertilizers used out of animal manure")
} else if(input$Cropsys_choice == "Fruit trees - Young plantations"){
  cat("Uncommon cropping system (0.7% of the sample)\n
Fruit trees (Longan,Mangoes, Coconuts) in the upland, No production\n
Motivated by Market price and demand mostly except for mangoes (household consumption preferences + well adapted)\n
On average 1ha of Misc. fruit trees\n 
Only mowing slashing for Longan, for Coconuts:
- Water ponds, swales digging
- Crop residues to cover the soil
- Fertilization through animal manure, Recycling crop waste 	& Ramial Wood Chip (RWC) or other wood chips
- Weeding through mowing/slashing\n
For mangoes: Rainwater collection/conservation, Water-Ponds, Crop residues to cover the soil, Animal manure,
Mowing / slashing\n
High density:
- 100 trees/ha for Mangoes and Longan
- 200-300 trees/ha for Coconuts\n
For most kind of fruits: requiring water, for longan only: requiring heavy fertilization\n
\n
Assumptions:\n
- Fruit trees grown as cash crop by households with possibility to do so (knowledge, land, 
labor force, value chain access...) with high density,\n with many practices associated related to watering,
soil fertility and pest and disease management depending on the specie")}
} else if(input$Sarea_choice == "Lao"){
  if (input$Cropsys_choice == "Summer-autumn season rice with off-season vegetables"){
cat("Information:\n
Very common cropping system (39% of the households), grown because of household consumption preferences mainly (78%)
but also for market price and demand (16%)\n
0.5-2ha of rice (do not know if broadcasted or transplanted), 48% of farmers use animal manure,
17% do swales digging\n
Average sowing amount (around 80-120 kg/ha), high yield (3-5 t/ha)\n
3/4 of the households are selling rice, on average 35% of the harvest. Many households (> 50%) think it requires important
amount of fertilizer\n

Vegetables/misc. crops are grown on the same plot, on lower area  on the same year (assumption), some are very common
across the sample:
- Garlic (31.5% of N study - For commercial and consumption purposes, >0.5 fertilize it with animal manure)
- Chinese lettuce (16.4% of N study - For commercial and consumption purposes, >0.5 fertilize it with animal manure)
- Chili (9.5% of N study -  For commercial and consumption purposes, >0.5 fertilize it with animal manure)

Other species are less common:
- Onions (4% of N study - Mainly for commercial purposes)
- Coriander (2.2% of N study - Mainly for commercial purposes)
- Peanut (2.2% of N study - For commercial purposes)
- Cucumber (1.5% of N study - For commercial purpose)
- Salad/lettuce (1.3% of N study - For commercial and consumption purposes)
- Long bean (1.3% of N study - For commercial purposes)
- Spring onions (0.9% of N study - For commercial purpose)
- Cabbages (0.9% of N study - For commercial purpose)
- Napa Cabbages (0.7% of N study - For commercial purpose)
- Kale flower (0.7% of N study - For commercial and consumption purposes)
- Chinese flowering Cabbages/ choysum (0.5% of N study - For commercial and consumption purposes)
- Mustard greens (1.5% of N study - For commercial and consumption purpose, Animal manure for 50% of the sample)
- Dill (0.2% of N study - For commercial purpose)
- Red bell pepper (0.2% of N study - For commercial purpose)
- Mung bean (0.2% of N study - For commercial purpose)
- Carrot (0.2% of N study - For commercial purpose)
- Hmong Cucumber (0.2% of N study - For commercial and consumption purposes)
- gourd (0.2% of N study - For consumption purposes)

AE practices are implemented for a non-negligible share of households for each crops, for water conservation
(ponds, swales digging, rainwater collection), soil fertility (animal manure, compost) and weed management (misc.)

\n
Assumptions:\n
- This cropping system is very common in area with good access to the lowland (Pek and Phoukoud district)
- It aim to provide food for household consumption (rice and vegetables) and livelihood through the selling of 
off-season vegetables which seems to be more a commercial crop, and rice surplus\n
- AE practices are commonly used for rice and vegetables, by at least a share of the concerned farmers, as these
cropping systems are central for household livelihood
- No real clue about use of pesticides (herbicides), potential use of
fertilizer despite animal manure is often used as yields seems important\n
")
} else if(input$Cropsys_choice == "Summer-autumn season rice"){
  cat("Information:\n
Very common cropping system (39% of the households), grown because of household consumption preferences mainly (78%)
but also for market price and demand (16%)\n
0.5-2ha of rice (do not know if broadcasted or transplanted), 43% of farmers use animal manure,
28% do swales digging and 25% collect rainwater\n
Average sowing amount (around 85-110 kg/ha), high yield (3-5 t/ha)\n
Half of the households are selling rice, on average 40% of the harvest. Many households (> 50%) think it requires
important amount of fertilizer\n

Assumptions:\n
- This cropping system is very common in area with good access to the lowland (Pek and Phoukoud district)
- It aim to provide food for household consumption (rice) and livelihood through the selling of rice surplus\n
- For now ni clue about why these households are not growing vegetables as the previous ones
- No real clue about use of pesticides (herbicides), potential use of fertilizer despite animal manure is often used
as yields seems important\n")
} else if(input$Cropsys_choice == "Vegetables (lowland or upland)"){
  cat("Information:\n
  Vegetables/misc. crops grown on small area (various but around 0.2ha):

- Chinese lettuce (4.2% of N study - Upland and lowland - For commercial and consumption purposes, 
>0.5 fertilize it with animal manure)
- Garlic (2.6% of N study - Upland and lowland - For commercial and consumption purposes, Animal manure used by >75%)
- Chili (1.7% of N study - Upland or lowland -  For commercial and consumption purposes, 0.4-0.5 
fertilize it with animal manure)
- Onions (1.1% of N study - Mainly for commercial purposes, Animal manure for 100% of households)
- Pumpkin (0.9% of N study - Upland - For commercial and consumption purposes)
- Coriander (0.8% of N study - Upland and lowland - For commercial and consumption purposes, Animal manure 
for 100% of households)
- Napa Cabbages (0.7% of N study - For commercial purpose, Animal manure for 50% of households)
- Cucumber (0.6% of N study - Upland & lowland - For commercial and consumption purposes, Animal manure 
for 75% of households)
- Chinese flowering Cabbages/ choysum  (0.2% of N study - Mainly for commercial purposes, Animal manure 
for 100% of households)
- Hmong Cucumber (0.4% of N study - For consumption purposes)
- Eggplant (0.2% of N study - Upland - For consumption purposes)
- Mustard greens (0.2% of N study - Upland - For consumption purposes)
- Spring onions (0.2% of N study - For commercial purpose, 100% use animal manure)
- Salad/lettuce (0.2% of N study - For commercial purpose, 100% use animal manure)
- Kale flower (0.2% of N study - Upland - For commercial and consumption purposes, 100% use animal manure)
- Long bean (0.2% of N study - Upland - For consumption purposes)
- Taro (0.2% of N study - Upland - For commercial purposes)
- Chinese plantain, leaves (0.2% of N study - For consumption purposes)

AE practices are implemented for a non-negligible share of households for each crops in the lowland,
less in the upland, for water conservation (ponds, swales digging, rainwater collection),
soil fertility (animal manure, compost) and weed management (misc.)

\n
Assumptions:\n
- Vegetables are grown for commercial and consumption purposes in lowland and upland areas\n
- AE practices are commonly used for vegetables, by at least a share of the concerned farmers, as these cropping systems 
are important for livelihood and self-sufficiency\n
")
} else if(input$Cropsys_choice == "Cassava monocropping"){
  cat("Not represented enough to be detailed\n")
} else if(input$Cropsys_choice == "Strawberry"){
  cat("Information:\n
  Strawberry grown on small area (various but around 0.02 - 0.1ha) by a small share of households in upland or lowland areas 
(1.9% of households)\n
Commercial crop moslty grown for commercial purposes\n
50% of farmers use animal manure\n
Many households (almost 50%) think it requires important amount of fertilizer\n

Assumptions:\n
- This cropping system is practiced by a small share of households in areas with access to lowland or upland for 
commercial purpose\n")
} else if(input$Cropsys_choice == "Fruit trees - Productive plantations"){
cat("Information:\n
Plum or Peaches grown on average area (various but around 0.5 - 1.5ha) by a small share of households (2% of households)
, moslty grown for commercial purposes\n
No AE practices except weeding\n

Assumptions:\n
- This cropping system is practiced by a small share of households for commercial purpose in areas including good upland 
and lowland access (mostly Phoukoud and Pek\n")
} else if(input$Cropsys_choice == "Peanut monocropping"){
cat("Information:\n
Crop grown on small area (various but around 0.2ha) by a small share of households (1.5% of households)
, moslty grown for commercial purposes\n
Few AE practices\n

Assumptions:\n
- This cropping system is practiced by a small share of households for commercial purpose in remote areas with mainly upland
access (Pek district)\n")
} else if(input$Cropsys_choice == "Job tears monocropping"){
cat("Information:\n
Crop grown on average area (various but around 1-1.5ha) by a medium share of households (5.3% of households)
, moslty grown for commercial purposes\n
Few AE practices for most of the growers\n

Assumptions:\n
- This cropping system is practiced by a medium share of households for commercial purpose in remote areas with mainly upland 
access (Pek district)\n")
} else if(input$Cropsys_choice == "Ginger monocropping"){
cat("Information:\n
Crop grown on average area (various but around 1ha) by a small share of households (2% of households)
, moslty grown for commercial purposes (some plantations seems not productive)\n
Few AE practices for most of the growers\n

Assumptions:\n
- This cropping system is practiced by a small share of households for commercial purpose in remote areas with mainly
upland access (Pek district)\n")
} else if(input$Cropsys_choice == "Upland rice monocropping"){
cat("Information:\n
Crop grown on average area (various but around 1ha) by an important share of households (14.6% of households)
, moslty grown for consumption purposes\n
Average sowing density (50-100) and yield (around 2.5 t/ha)\n
26% of these households are selling a share of their production\n
Few AE practices for most of the growers\n

Assumptions:\n
- This cropping system is practiced by most households in remote areas with mainly upland access (Pek district)
as base of food system (equivalent of lowland rice in other districts\n
- Some households have enough land to sell a small share of the production\n")
} else if(input$Cropsys_choice == "Tea plantation"){
cat("Information:\n
Crop grown on average area (various but around 1ha) by an important share of households (13.5% of households)
, moslty grown for commercial purposes\n
91% of these households are selling a share of their production (there are unproductive plantation)\n
Few AE practices for most of the growers\n

Assumptions:\n
- This cropping system is practiced by most households in areas with lowland and upland access(Phoukoud and Kham district) 
as commercial crop\n
- For now no clue about why only a share of households in these areas are growing tea, potentially because 
of not enough land access ?\n")
} else if(input$Cropsys_choice == "Traditionnal maize - consumption and selling"){
cat("Information:\n
Crop grown on small area (various but around 0.1ha) by a small share of households (1.1% of households), moslty grown for consumption  purposes\n
No households are selling a part of their production\n
50% of households are mowing/slashing\n
Low yield: 2.5 t/ha\n

Assumptions:\n
- This cropping system is practiced by a small share of households in areas with lowland access (Phoukoud and Kham district)
as consumption crop\n")
} else if(input$Cropsys_choice == "Traditionnal maize - consumption"){
cat("Information:\n
Crop grown on small area (various but around 0.5ha) by a small share of households (1% of households),\n
moslty grown for commercial purposes (All are selling, 80% of the production)\n
Many AE practices, Water, soil fertility and weeding, 60% of households are using animal manure\n
AVerage yield: 3.3 t/ha\n

Assumptions:\n
- This cropping system is practiced by a small share of households in areas with lowland access (Phoukoud and Kham district)
as commercial crop\n")
} else if(input$Cropsys_choice == "Hybrid maize - selling"){
cat("Information:\n
Crop grown on average area (around 2ha) by an important share of households (22% of households),
moslty grown for commercial purposes\n
Few AE practices\n
Average yield: 4.4 t/ha\n

Assumptions:\n
- This cropping system is practiced by most households in remote areas with mostly upland access (Pek district) 
as commercial crop\n
- Potential use of herbicides and chemical fertilizer for fertility maintenance")}
} else if(input$Sarea_choice == "Son La province"){
  if (input$Cropsys_choice == "Rice with off-season vegetables") {
cat("Information:\n
Uncommon cropping system (1.4% of the sample), we assume vegetables and rice are grown on the same plot (not confirmed)\n
FOR RICE:
small area of rice: around 0.2ha (no details if broadcasted or transplanted), Few AE practices except biopesticides used by
50% of households\n
No part of the production is sold\n
Average sowing amount for rice (around 80-100 kg/ha), high yield (around 6 t/ha)\n
FOR VEGETABLES:
-	Winter melon (0.4% of N study – 0.3ha – 100% of h are selling) – Ponds and rainwater collection for all households
-	Cucumber (0.4% of N study – 0.3ha – Commercial 100%) – Ponds, biopesticides and pheromone traps for all households
-	Pumpkin (0.2% of N study – 0.2ha – Commercial mostly) – Access to water through ponds 
or natural water source for 100%

Assumptions:\n
- Rice grown for household consumption (150-200kg/hmember/year), small area but high yields showing high 
labor/inputs investment on these plots\n
- Use of pesticides (herbicides) and fertilizer likely as high yields and no animal manure use reported\n")}
  if (input$Cropsys_choice == "Winter-spring season rice") {
cat("Information:\n
Uncommon cropping system (3.5% of the sample)
Small area of rice: around 0.1ha (no details if broadcasted or transplanted),
Patch/ban spraying practiced by >50% of households\n
No part of the production is sold\n
Sowing density highly variable for rice (75 to 200kg/ha), very high yields (around 7 t/ha)\n
\n
Assumptions:\n
- Rice grown for household consumption (150-200kg/hmember/year), small area but high yields showing high 
inputs/labor investment on these plots\n
-Use of pesticides (herbicide if broadcasted) and fertilizers fairly likely as high yields and no animal manure use reported\n
- Difficult to know why these households are growing only one rice cycle, maybe because of lack of access
to water or lack of labor or no need of additionnal production\n")}
    if (input$Cropsys_choice == "Summer-autumn season rice") {
cat("Information:\n
Moderately common cropping system (7% of the sample)
average area of rice: around 0.35ha (no details if broadcasted or transplanted),
Use of biopesticides and mulching for >20% of households\n
No part of the production is sold\n
Sowing density highly variable (50 to 150kg/ha), high yields (around 4.7 t/ha)\n
\n
Assumptions:\n
- Rice grown for household consumption (150-200kg/hmember/year), small area but high yields showing high inputs/labor
investment on these plots\n
-Use of pesticides (herbicide if broadcasted) and fertilizers fairly likely as high yields and no animal manure use reported
- Difficult to know why these households are growing only one rice cycle, maybe because of lack of access to water 
or lack of labor or no need of additionnal production\n")}
    if (input$Cropsys_choice == "Summer-autumn and winter-spring season rice") {
cat("Information:\n
Common cropping system (30.8% of the sample)
Small area of rice: around 0.15ha for each kind (no details if broadcasted or transplanted),
Few AE practices used\n
A small part of the househols (20%) sell on average 50% of their production for both kind of rice\n
SUMMER AUTUMN SEASON RICE:
Sowing density highly variable (50 to 100kg/ha), high yields (around 5.5 t/ha)\n
WINTER SPRING SEASON RICE:
Sowing density highly variable (50 to 100kg/ha), high yields (around 6 t/ha)\n
\n
Assumptions:\n
- Rice grown two times per year on the same plot for household consumption (150-200kg/hmember/year), small area
but high yields (and double rice cycle) showing high inputs/labor investment on these plots\n
-Use of pesticides (herbicide if broadcasted) and fertilizers fairly likely as high yields and no animal manure use reported\n
- A part of the households are able to sell a part of their production as they produce enough for themself and a surplus,
maybe they have access to higher area or can invest more labor/inputs on their land\n")}
    if (input$Cropsys_choice == "Vegetables (lowland)") {
cat("Information:\n
Moderately common - 11.5% of h - Vegetables/misc. crops grown on small area (various but around 0.1-0.2ha):
-	Cucumber (1% of N study - 0.1ha – Commercial 100%) - USe of animal manure and Access to water through ponds or
natural water source for 2/3 – Biopesticides and pheromones trap for part of households
-	Mustard greens (4% of N study – 0.07 ha – Commercial 100%) – Access to water through ponds or natural water source
for 80%, animal manure for 50% and mowing/slashing for 2/3 – Biopesticides and bioherbicides for part of households
-	Spring onions (7% of N study – 0.17ha – Commercial 100%) - Access to water through ponds or natural water source
for >60% - Biopesticides and bioherbicides for part of households
-	Coriander (2% of N study – 0.1ha – Commercial 100%) - Access to water through ponds or natural water source for 100%
and mowing slashing for 2/3, biopesticides for 2/3 – Bioherbicides for part of households
-	Chinese flowering cabbage/choysum (0.7% of N study – 0.05ha – Commercial 100%) - Access to water through ponds
or natural water source for 100% and animal manure for 100%
-	Cabbages (0.6% of N study – 0.6ha – Commercial 100%) – Rainwater collection/conservation, Animal manure,
Bokashi (fermented organic matter), Bioherbicide, Biopesticide / organic pesticide for 100% of the
households in these systems
-	Winter melon (0.7% of N study – 0.25ha – Commercial 100%) – Rainwater collection for all and ponds for >50%
-	Hmong mustard (5.3% of N study – 0.08ha – Commercial 100%) - Access to water through ponds or natural water source for 100%
-	Tomato (1.3% of N study – 0.07ha – Commercial 100%) – Access to water through ponds or natural water source and
use of Patch/ban spraying for weeds for 50%
-	Local bean (0.7% of N study – 0.07ha – Commercial 100%) – Use of Patch/ban spraying for 100%
-	Local mustard (1.3% of N study – 0.03ha – Commercial 100%) – Access to water through ponds or natural water source,
use of animal manure and mowing slashing for 100% - Use of Bioherbicide, Biopesticide / organic pesticide 
for 50% of the sample
-	French bean (1.6% of N study – 0.35ha – Commercial 100%) – Many AE practices but for a small part of the sample
-	Zucchini, common green, fruit (0.6% of N study – 0.35ha – Commercial 100%) – Rainwater collection/conservation,
use of animal manure, bokashi (fermented organic matter), Bioherbicide and Biopesticide / organic pesticide 
for 100% of households
\n
Assumptions:\n
- Vegetables are grown for commercial purposes in lowland areas\n
- AE practices are commonly used for vegetables, often by a majority of the concerned farmers, as these 
cropping systems are important for livelihood\n")}
    if (input$Cropsys_choice == "Vegetables (upland)") {
cat("Information:\n
Moderately common (16% of h) - Vegetables/misc. crops grown on medium area (various but around 0.2-1ha):
-	Cabbages (4.9% of N study – 0.4 ha – Commercial 100%) – Animal manure and mowing/slashing for > 60% of households
– Bokashi, biopesticides for part of households
-	Cucumber (0.3% of N study – 0.2 ha – Commercial 100%) – water ponds, animal manure, mowing/slashing, biopesticides
for 100% of households
-	Potatoes (0.1% of N study – 0.3 ha – Commercial 100%) – Ponds, Swales digging, Crop residues maintained 
to cover the soil, Animal manure, Bokashi (fermented organic matter), Biopesticide / organic pesticide 
for 100% of the households
-	Pumpkin (0.7% of N study – 1.11 ha – Most of the production is sold) - Rainwater collection/conservation,
Swales digging, Crop residues maintained to cover the soil, Crop residue maintenance, Mowing / slashing 
for app. 50% of the households
-	Winter-melon (3.4% of N study – 0.4ha – Most of the production is sold) – Animal manure used by 50% 
of the households\n
\n
Assumptions:\n
- Vegetables are grown for commercial purposes in upland areas\n
- AE practices are commonly used for vegetables, often by a majority of the concerned farmers, as these cropping
systems are important for livelihood\n")}
    if (input$Cropsys_choice == "Maize biomass (commercial)") {
cat("Information:\n
Crop grown in lowlands or uplands on average area (various but around 0.5-1 ha) by a small share of households
(5% of households)\n
Grown for commercial purposes (All are selling most of their production)\n
Few AE practices, half of the
households have access to water to grow this crop\n
Average yield: 7 t/ha\n
\n
Assumptions:\n
- Use of chemical fertilizer as no use of animal manure\n")}
    if (input$Cropsys_choice == "Maize grain - Consumption") {
cat("Information:\n
Crop grown in lowlands or uplands on average area (0.1-1 ha) by a medium share of households (8% of households)\n
Grown for consumption purposes only\n
Few AE practices (reduced to no-tillage for 0.1 of them)\n
Average yield: 6.5 t/ha\n

Assumptions:\n
- Use of corn to self-consume or feed the animals, not possible to sell some as not enough land
- Use of chemical fertilizer as no use of animal manure\n")}
    if (input$Cropsys_choice == "Maize grain - Consumption and selling") {
cat("Information:\n
Crop grown in lowlands or uplands on average area (1-2 ha) by an important share of households (39% of households)\n
Grown for commercial purposes mainly (85% of the production is sold on average)\n
Few AE practices (Patch/ban spraying use for weeding for 0.25 of them)\n
Average yield: 8.5 t/ha\n
\n
Assumptions:\n
- Corn is grown on large areas in the lowlands and uplands as a cash crop\n
- Use of chemical fertilizer 
as no use of animal manure and high yields, likely use of pesticides\n")}
    if (input$Cropsys_choice == "Ginger monocropping") {
cat("Information:\n
Crop grown in uplands on small area (around 0.07 ha) by a small share of households (1.4% of households)\n
Grown for commercial purposes only (all the production is sold)\n
63% of households are mulching, 37% are doing agroforestry (trees + crops), 26% are using cover crops and biopesticide
/ organic pesticide\n 
\n
Assumptions:\n")}
      if (input$Cropsys_choice == "Tea plantation") {
cat("Information:\n
Crop grown on small area (around 0.5 ha) by a medium share of households (11.5% of households)\n
Grown for commercial purposes only (all the production is sold) but there are also non-productive plantations\n
Mowing/slashing for 50% of households \n 
Many AE practices by a small share of households (<30% : Rainwater collection/conservation, Ponds
(for water conservation),
Sowing in contour lines, Animal manure, Bokashi (fermented organic matter), Patch/ban spraying, AEP Weed-Bioherbicide,
Biopesticide / organic pesticide)\n
\n
Assumptions:
- This crop is grown as cash crop by a minority of households as it requires access to the uplands
- AE practices are commonly used for this crop as these cropping systems are important for household livelihood\n")}
      if (input$Cropsys_choice == "Cassava monocropping - consumption & selling") {
cat("Information:\n
Crop grown on variable area (around 1-2ha in Tan Hop com. and around 0.5ha in other communes) by a high share
of households (23.2% of households)\n
Grown for commercial purposes mainly (96% of the production is sold)\n
Rainwater collection/conservation
for 44%\n
High yield: 17.5 t/ha on average\n
\n
Assumptions:
- This crop is grown as cash crop by a minority (but still important amount) of households as it requires access to the uplands\n
- A small part of the production is self-consumed or used as animal feed\n
- Likely use of chemical fertilizers as no other fertility management\n")}
      if (input$Cropsys_choice == "Cassava monocropping - consumption") {
cat("Information:\n
Crop grown on small area (around 0.1ha) by a small share of households (2.4% of households)\n
Grown for consumption purposes only, no share of the production is sold\n
21% used Animal manure or patch/ban spraying\n
High Yield: 25 t/ha\n
\n
Assumptions:
- Crop grown by households with upland access as consumption crop\n
- Likely use of chemical fertilizers as no other fertility management\n")}
      if (input$Cropsys_choice == "Upland rice monocropping") {
cat("Information:\n
Crop grown on small area (around 0.2ha) by a small share of households (5.5% of households)\n
Grown for consumption purposes only, no share of the production is sold\n
No AE practice\n
Medium sowing density: around 100 kg/ha and medium Yield: around 3.5 t/ha\n
\n
Assumptions:
- Crop grown by households with upland access as consumption crop\n
- Likely use of chemical fertilizer and herbicides as no other fertility and weed management practices\n")}
      if (input$Cropsys_choice == "Arrowroot monocropping") {
cat("Information:\n
Crop grown on small area (around 0.2ha) by a small share of households (4.4% of households)\n
Grown for commercial purposes mainly, some plantations seems not yet productive as only  90% of households are selling it\n
AE practices for a small part of the households (Rainwater collection/conservation, Mulching,
Patch/ban spraying and Mowing / slashing)\n
\n
Assumptions:\n")}
      if (input$Cropsys_choice == "Fruit trees - Productive plantations") {
cat("Information:\n
Very common cropping system as 53% of the households have fruit trees (including productive and non-productive plantations) 
on medium area (around 0.4-0.5ha)\n
Grown for commercial purposes mainly as most of the production is sold for most of the different kinds of fruit trees\n
Some species are common across the sample:\n
- Apricot (7% if h – 0.37ha - 100% sold) – Mowing/slashing for 40% of households,
A part of households are doing agroforestry and use of pulses\n
- Plum (23.2% of h – 0.54 ha – almost 100% sold) - Mowing slashing for 36% of households
Use of biopesticides and/or agroforestry\n
- Mango (22.2% of h – 0.57 ha -  80% of households are selling) – Many AE practices for small part of the sample\n
- Longan (21.7% of h – 0.7 ha – 95% of households are selling all of their production)
Mowing/slashing for 54% of the sample, bioherbicides and biopesticides for small part of the sample\n
Some species are less common:\n
- Chayote (7.3% of h - 0.3 ha - Most households are selling most of their production)
Animal manure and mowing/slashing used by >50% of the households, many other AE practices used by a small share of households\n
- Avocado (3.4% of h - 0.035ha - 70% of households are selling their production)
Use of ponds for 60% of households and mowing/slashing for 90% of them, many other AE practices for a small share of the sample\n
- Coconut (2.1% of h - 0.2 ha - Commercial purpose only)
42% of the households are mulching, many AE practices for a small part of the sample\n
- peach (1.4% of h - 0.4 ha - 75% of households are selling all of their production)
Use of ponds and mulching for almost 40% of households\n
- Oranges (1.3% of h - 0.4 ha - Commercial purpose only)
Ponds (for water conservation) and animal manure used by 76% of the households
Reduced to no-tillage and mowing/slashing used by >50% of the households
Other AE practices used by a small share of the sample\n
- Passion fruit (0.3% of h - 0.15 ha - Commercial purpose only)
Ponds used by 100% of h\n

Assumptions:
- Fruit trees grown as cash crop by half of total households, meaning it is a very important commercial crop in this area\n
- Many AE practices associated related to watering, soil fertility and pest and disease management depending on the
specie as important source of income for households\n
- Few households are not selling while they have productive plantation meaning they likely self-consume their production\n")}
     if (input$Cropsys_choice == "Fruit trees - Young plantations") {
cat("Information:\n
Very common cropping system as 53% of the households have fruit trees (including productive and non-productive
plantations) on medium area (around 0.4-0.5ha)
These plantation aren't yet productive
Some species are common across the sample\n:
- Apricot (6.3% if h – 0.35ha) – Mowing/slashing for 28% of households\n
- Plum (6.1% of h – 0.2 ha) - Mowing slashing for 32% of households
Agroforestry for 20%\n
- Mango (7% of h – 0.15 ha) – Many AE practices for small part of the sample\n
- Longan (4.8% of h – 0.2 ha) - Many AE practices for small part of the sample\n
Some species are less common:\n
- Avocado (1.4% of h - 0.35ha)
Mowing/slashing for 25% of households\n
- Jack fruit (1.2% of h - 0.04 ha)
bioherbicide, mowing / slashing and biopesticide / organic pesticide 	used by 55% of these households\n
- peach (1% of h - 0.1 ha) - Patch/ban spraying and Mowing / slashing for 50% of the households\n
- Pomelos and grapefruit (0.2% of h - 0.015ha) - No AE practices\n

Assumptions:\n
- Fruit trees grown as cash crop by half of total households, meaning it is a very important commercial crop in this area,
Here it is non-productive trees (likely young plantation)\n
- Few AE practices associated contrarily to the productive plantations\n")}
}else{
    if (input$Cropsys_choice == "Rice with off-season vegetables") {
cat("Information:\n
Common cropping system (24.1% of the sample), we assume vegetables and rice are grown on the same plot (not confirmed)
FOR RICE:
small area of rice: around 0.2ha (no details if broadcasted or transplanted),
It can be summer-autumn season
rice or winter-spring season rice\n
Animal manure used by 30% of households,Patch/ban spraying and biopesticides used by a small part of the households\n
Half of their harvest sold by >40% of the households\n
Average sowing amount for rice (around 100 kg/ha), high yield (around 5.4 t/ha)\n
\n
FOR VEGETABLES:
- Cabbages (9.3% of h - 0.05ha - Commercial for most households) - Swales digging used by 31% of the households,
animal manure used by 45% of the households, other AE practices used by a small share of the households\n
- Sweet potatoes, tuber (5.7% of h - 0.23ha - 100% Commercial) - 34% of households use animal manure,
other AE practices are used by a small share of households\n
- Eggplant (4.8% of h - 0.08ha - 100% Commercial) - Around 30% of the h: Swales digging, Animal manure, Mowing / slashing\n
-	Cucumber (2.6% of N study – 0.06ha – 100% of h are selling) – Animal manure used by 30% of the households,
other AE practices used by small share of households\n
- Spring onions (2% of N study - 0.016ha - Mostly a commercial crop) - 
Swales digging, animal manure,
Patch/ban spraying, Biopesticide / organic pesticide used by 34% of households, other AE practices used by small share of the sample\n
- Cauliflowers, Broccoli (1.6% of h - 0.02ha - 100% Commercial) - Swales digging (66%), Animal manure (78%),
Patch/ban spraying (56%), Biopesticide / organic pesticide (66%)\n
- Pumpkin (1.5% of h - 0.13ha - 100% commercial) - Animal manure 	used by 79% and Patch/ban spraying used by 58% of households,
Many other AE practices used by a small share of the households\n
- Chinese kale/ Gailan (1.4% of h - 0.01ha - Commercial and self consumption purposes) - Few AE practices\n
- Tomato (1.3% of h - 0.035ha - 100% commercial) - Swales digging and animal manure used by >50% of the households,
other AE practices used by small share of the households\n
- Hmong mustard (1.3% of h - 0.01ha - Commercial and self consumption purposes) - Ae practices used by a small share of the households\n
-	Mustard greens (1.2% of N study – 0.015ha – Commercial and self consumption 50/50) – Animal manure used by 40% of
the households, other AE practices used by small share of households\n
- Garlic (0.7% of h - 0.015ha - Self consumption only) - Crop residues maintained to cover the soil for 53% of these households\n
-	Mung bean (0.6% of N study – 0.025ha – Commercial and self consumption 50/50) – Animal manure and mowing/slashing
used by 50% of the households%\n
- Potatoes (0.6% of h - 0.05ha - 100% commercial) - Animal manure used by 50% of the households\n
- Kudzu (0.6% of h - 0.014ha - Self-consumption only) - No AE practice\n
- Chrysanthemum, leaves (0.5% of h - 0.02ha - Self-consumption) - Crop residues maintained to cover the soil and
animal manure used by 34% of the households\n
- Local mustard (0.5% of h - 0.01ha - Commercial and self-consumption purposes) - No AE practices\n
- Chinese flowering Cabbages/ choysum (0.5% of h - 0.005 - Selling and self consumption) - Animal manure and
Legume-based green manure for 37% of the households\n
- Mustard (0.4% of h - 0.013ha - 100% commercial) - Animal manure and legume-based green manure for 50% of the households\n
- Black bean (0.4% of h - 0.05ha - 100% commercial) - Patch/ban spraying used by 100% of the households/n
- Lettuce, romaine, leaves (0.4% of h - 0.001ha - Commercial and self consumption purposes) - No AE practices\n
- Long bean, Chinese (0.4% of h - 0.3ha - 100% commercial) - No AE practice\n
- French bean (0.3% of h - 0.04ha - 100% commercial) - No AE practice\n
- Carrot (0.3% of h - 0.02ha - 100% commercial) - Animal manure used by 100% of the households\n
- Pak choy (0.3% of h - 0.01ha - Self consumption only) - Swales digging and mowing/slashing for 100% of the households\n
- Winter melon (0.3% of h - 0.1ha - Commercial for most household) - Animal manure used by 100% of the households\n
- Honeydew (0.3% of h - 0.03ha - 100% commercial) - No AE Practice\n
- Basil, sweet, leaves (0.3% of h - 0.05ha - 100% Commercial) - For 100% of the households: Swales digging,
Animal manure, Patch/ban spraying, Biopesticide / organic pesticide\n
- Kidney bean (0.3% of h - 0.05ha - 100% Commercial) - For 100% of the households: Swales digging,
Animal manure, Patch/ban spraying, Biopesticide / organic pesticide\n
- Local bean (0.2% of h - 0.005ha - Commercial for most households) - No AE practices\n
- Turmeric, root (0.2% of h - 0.1ha - 100% commercial) - Animal manure used by 100% of the households\n
\n
Assumptions:\n
- Rice grown for household consumption (150-200kg/hmember/year), small area but high yields showing high
labor/inputs investment on these plots\n
- Use of pesticides (herbicides) and fertilizer likely as high yields and no animal manure use reported\n
- Vegetables grown on the same plot for commercial purposes, high variety of vegetables\n
- Many AE practices used for vegetables, as it seems to be an important crop for household income\n")}
        if (input$Cropsys_choice == "Summer-autumn season rice") {
cat("Information:\n
Crop grown on small area (around 0.4ha) by a medium share of households (7% of households) (no details if
broadcasted or transplanted)\n
Grown for consumption purposes mainly (13% of h are selling it)\n
Important sowing density:
100-120 kg of seeds/ha , high yield: 4.6 t/ha\n
Animal manure used by 20% of the households, other AE practices used by a small share of the households\n
\n
Assumptions:\n
- Rice grown for household consumption (150-200kg/hmember/year), small area but high yields showing high
inputs/labor investment on these plots\n
-Use of pesticides (herbicide if broadcasted) and fertilizers fairly likely as high yields and only 1/3 of
the households use animal manure\n
- Difficult to know why these households are growing only one rice cycle, maybe because of lack of access to water
or lack of labor or no need of additionnal production\n")}
          if (input$Cropsys_choice == "Winter-Spring season rice") {
cat("Information:\n
Crop grown on small area (around 0.33ha) by a small share of households (2.4% of households) (no details
if broadcasted or transplanted)\n
Grown for consumption and commercial purposes (Half of the households are selling half of their production)\n
Important sowing density: 90-130 kg of seeds/ha , very high yield: 5.5 t/ha\n
Sowing in contour lines used by 35% of the households and animal manure used by 32% of the households\n
\n
Assumptions:\n
- Rice grown for household consumption (150-200kg/hmember/year) and commercial purposes (for the surplus),
small area but high yields showing high inputs/labor investment on these plots\n
-Use of pesticides (herbicide if broadcasted) and fertilizers fairly likely as high yields and only 1/3 of
the households use animal manure\n
- Difficult to know why these households are growing only one rice cycle, maybe because of lack of access to water
or lack of labor or no need of additionnal production\n")}
            if (input$Cropsys_choice == "Summer-autumn and winter-spring season rice") {
cat("Information:\n
Crop grown on small area (around 0.2ha) by a large share of households (58% of households) (no details if
broadcasted or transplanted)\n
Two cycles of rice grown consecutively during winter-spring and then summer-autumn\n
Grown for consumption and commercial purposes (Half of the households are selling half of their production for
winter-spring and around 0.2/0.2 for summer-autumn which is lilely more self-consumed)\n
Average sowing density: 80-100 kg of seeds/ha , very high yield: 5.6 t/ha\n
Sowing in contour lines
used by 37% of the households and mowing/slashing used by 26% of the households\n
\n
Assumptions:\n
- Rice grown 2 times per year on the same plot, mainly for household consumption (150-200kg/hmember/year)
and commercial purpose (for the surplus), small area but high yields showing high inputs/labor 
investment on these plots\n
-Use of pesticides (herbicide if broadcasted) and fertilizers fairly likely as high yields and only 1/3
of the households use animal manure\n")}
  if (input$Cropsys_choice == "Vegetables (upland)") {
cat("Information:\n
Common cropping system (1.5% of the sample) on small areas (0.01-0.05ha)\n
Species concerned:
- Sawtooth herb/culantro (0.3% of h - 0.01ha -100% commercial)
100% of the households are practicing:
Swales digging, Animal manure, Patch/ban spraying, Biopesticide / organic pesticide\n
- Sweet potatoes, leaves (0.3% of h - 0.03ha - Self-consumption) - 100% of the households are practicing: 
Patch/ban spraying and Biopesticide / organic pesticide
- Kohlrabi (2.6% of h - 0.05ha - Commercial for most households) - Swales digging used by 40%, animal manure
used by 56% and Patch/ban spraying used by 35% of the households, other AE practices used by a small share of the households\n
- Eggplant (0.6% of h - 0.06ha - 100% commercial) - 100% of the households use: Patch/ban spraying and Biopesticide
/ organic pesticide
50% of the households use Rainwater collection/conservation and animal manure\n
\n
Assumptions:\n
- These vegetables are mainly grown for commercial purposes but also self-consumed by some households\n
- Many AE practices used for vegetables, as it seems to be an important crop for household income")}
              if (input$Cropsys_choice == "Cassava monocropping") {
cat("Information:\n
Crop grown on medium area (around 1ha) by a large share of households (32.5% of households)\n
Grown mainly for commercial purposes (92% of households are selling 90% of their production) a small part is self-consumed\n
Sowing in contour lines and mowing/slashing for 1/3 of the households\n

Average yield: 10 t/ha and variable but high sowing density\n
\n
Assumptions:\n
- Cassava grown as cash crop with high density and medium yield\n
- Use of herbicides/mechanical weeding for households who are not using mowing/slashing and fertilizers
for those who do not use animal manure\n")}
                if (input$Cropsys_choice == "Fruit trees - Productive plantations") {
cat("Information:\n
Uncommon cropping system as 2.6% of the households have fruit trees (including only productive fruit trees)
on low area (around 0.02-0.2ha)\n
Grown for commercial purposes mainly as most of the production is sold for most of the different kinds of fruit trees\n
Include different species\n:
- Bananas (0.4% of h – 0.02ha - 40% sold, part is self-consumed) – No AE practice\n
- Littchi (0.3% of h – 0.08 ha – 100% Commercial) - Practiced by 100% of the households: Animal manure, Mowing / slashing and
Use of biopesticides and/or agroforestry\n
- Longan (0.4% of h - 0.2ha - 100% commercial) - Practiced by 100% of the households: Patch/ban spraying,
Biopesticide / organic pesticide
- Oranges (0.7% of h - 0.2ha - 100% commercial) - For 55% of the households: Patch/ban spraying, Biopesticide / organic pesticide
For 45% of the households: Animal manure, Mowing/slashing
- Peach (0.3% of h - 0.03ha - 100% commercial) - For 100% of the households: Swales digging, Animal manure,
Nutrient placement,Patch/ban spraying,Biopesticide / organic pesticide 
- Pomelos and grapefruit (1.1% of h - 0.14ha - 100% commercial) - For 2/3 of the households: Patch/ban spraying,
Biopesticide / organic pesticide\n
\n
Assumptions:
- Fruit trees grown as cash crop by few household, potential link with access to labor or land\n
- Many AE practices associated highlighting it is likely an important source of income for households\n
- Part self-consumed for bananas\n")}
                  if (input$Cropsys_choice == "Fruit trees - Young plantations") {
cat("Information:\n
Uncommon cropping system as 0.7% of the households have young fruit trees
on low area (around 0.3ha)\n
No production yet, likely young plantation\n

Include only one specie\n:
- Pomelos and grapefruit, For 45% of the households: Animal manure and mowing/slashing\n
\n
Assumptions:
- Fruit trees grown as cash crop by few household, potential link with access to labor or land\n
- Less AE practices when compared with mature plantations\n")}
                if (input$Cropsys_choice == "Upland rice monocropping") {
cat("Information:\n
Crop grown on medium area (around 0.4ha) by a small share of households (4.3% of households)\n
Grown only for self-consumption purposes (no household is selling upland rice)\n
Mowing/slashing used by 1/3 of the households\n
Low yield: 2.7 t/ha and variable sowing density (\n
\n
Assumptions:\n
- Upland rice grown for self-consumption with medium-low yield\n
- Use of herbicides/mechanical weeding for households who are not using mowing/slashing and chemical
fertilizers for those who do not use animal manure\n")}
                  if (input$Cropsys_choice == "Maize grain - Consumption and selling") {
cat("Information:\n
Crop grown on small area (around 0.21ha) by an important share of households (21.2% of households)\n
Grown moslty for commercial purposes (All households are selling on average 85% of their production)\n
AE practices used by a small share of the households\n
Average yield: 6.3 t/ha \n
\n
Assumptions:\n
- Corn grown as a commercial crop with medium yields, grown on lowland and upland plots\n
- Use of herbicides/mechanical weeding for households who are not using mowing/slashing and chemical
fertilizers for those who do not use animal manure\n")}
  if (input$Cropsys_choice == "Maize grain - Consumption") {
cat("Information:\n
Crop grown on small area (around 0.1ha) by an important share of households (19% of households)\n
Grown moslty for self-consumption purposes\n
AE practices used by a small share of the households\n
Average yield: 5 t/ha \n
\n
Assumptions:\n
- Corn grown as a commercial crop with medium yields, grown on lowland and upland plots\n
- Use of herbicides/mechanical weeding for households who are not using mowing/slashing and chemical
fertilizers for those who do not use animal manure\n")}
    if (input$Cropsys_choice == "Maize biomass") {
cat("Information:\n
Crop grown on small area (around 0.14ha) by a small share of households (1.6% of households)\n
Grown for commerical and/or self-consumption purposes (2/3 are sellig, on average half of the production)\n
AE practices used by a small share of the households\n
Average yield: 4 t/ha \n
\n
Assumptions:\n
- Corn grown as a commercial crop and self-consumption (for animals) with medium yields, grown on
lowland and upland plots\n
- Use of herbicides/mechanical weeding for households who are not using mowing/slashing and chemical
fertilizers for those who do not use animal manure\n")}
}
  })
```


# Cultivation {data-navmenu="Cropping systems"}

## Row 1 {data-height=300}

### **General**

N Study area = **`r renderText({round(sum(All$SW_Weight[All$S_Area == input$Sarea_choice]), digits = 0)})`** / N Crop = **`r renderText({round(CropDesc$N[CropDesc$Sarea == input$Sarea_choice & CropDesc$Crop == input$Crop_choice], digits = 0)})`** / N cropsys = **`r renderText({round(Cropsys$N[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice], digits = 0)})`**\
**`r renderText({Cropsys$PerCentofHouseholds[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]*100})`%** of households grow this crop in this cropping system (% of N Study area) \
Average area = **`r renderText({round(Cropsys$'Area - m2'[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]/10000, digits = 3)})` ha**\
\
Main reason for growing this crop in this cropping system (% of N Crop):\
Household consumption preference: **`r renderText({Cropsys$"Reason% - Household consumption preferences"[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]*100})`**%\
Market price and demand: **`r renderText({Cropsys$"Reason% - Market price and demand"[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]*100})`**%\
Well adapted to local conditions: **`r renderText({Cropsys$"Reason% - Well adapted to local conditions"[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]*100})`**%

### **Main practices & AE practices implemented (>10% of N Crop)**
```{r}
renderTable({
AEP <- as.data.frame(t(Cropsys[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice,c(39:97)]))
colnames(AEP) <- "PerCent"
AEP = dplyr::filter(AEP, as.numeric(PerCent) >= 0.1)
AEP <- AEP %>% add_column("Category and practice" = rownames(AEP), .before = "PerCent")
print(AEP)
})
```



## Row 2 {data-height= 700}

### **Sowing amount distribution**
```{r}
  RnV$RiceTot <- RnV$`Summer-autumn season rice` + RnV$`Winter-Spring season rice`
  RnV$DR <- ifelse(RnV$`Summer-autumn season rice` > 0 & RnV$`Winter-Spring season rice` > 0, 1, 0)
  Rid <- RnV$hhid_re2[RnV$RiceTot > 0 & RnV$Lowveggie == 0 & RnV$DR == 0]
  RnVid <- RnV$hhid_re2[RnV$RiceTot > 0 & RnV$Lowveggie > 0]
  Vid <- RnV$hhid_re2[RnV$RiceTot == 0 & RnV$Lowveggie > 0]
  DRid <- RnV$hhid_re2[RnV$DR == 1 & RnV$Lowveggie == 0]
renderPlotly({
  columns_to_select <- ifelse(input$Sarea_choice == "Lao",     "district_eng_preload","commune_eng_preload")
  xlab <- ifelse(input$Sarea_choice == "Lao", "District","Commune")
  pattern <- paste0("d2_ha134.",input$Crop_choice)
  Area <- All %>% 
    filter(S_Area == input$Sarea_choice) %>%
      select("hhid_re2", all_of(columns_to_select), matches(input$Crop_choice))
  Area <- Area[!is.na(Area[,5]),]
    if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "No" | Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Norm" ){}else{
      if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Cons"){
        Area <- Area[is.na(Area[,10]) | Area[,10] == 0,] 
         }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Sell"){
          Area <- Area[Area[,10] > 0 & !is.na(Area[,10]),]
           }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Prod"){
            Area <- Area[Area[,14] > 0 & !is.na(Area[,14]),]
             }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "NoProd"){
              Area <- Area[is.na(Area[,14]) | Area[,14] == 0,]
           }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "R"){
            Area <- Area[Area$hhid_re2 %in% Rid,] 
            }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "RnV"){
             Area <- Area[Area$hhid_re2 %in% RnVid,]
             }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "V"){
              Area <- Area[Area$hhid_re2 %in% Vid,]
              }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "VnR"){
               Area <- Area[Area$hhid_re2 %in% RnVid & Area[,5] > 0,]
              }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "DR"){
               Area <- Area[Area$hhid_re2 %in% DRid & Area[,5] > 0,]
               }else{
                x <- strsplit(gsub("\"", "", Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]), ",")[[1]]
                Area <- Area[Area$hhid_re2 %in% x,]  
               }}
    Area <- Area %>% 
      select(all_of(columns_to_select), starts_with(pattern))
  ggplotly(
    ggplot(Area, aes(x = Area[,1], y = Area[,2], fill = Area[,1])) + 
    geom_boxplot() + 
    ggtitle(paste(input$Sarea_choice," - ",input$Crop_choice,"\n", input$Cropsys_choice, "\n Sowing amount - N = ", round(Cropsys$N[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice], digits = 0)))+
    theme(legend.position='none', plot.title = element_text(size = 10))+
    ylab(Cropsys$MSeedUnit[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice])+
    xlab(xlab)+
    scale_fill_viridis_d()
  )
})
```

### **Area distribution**
```{r}
renderPlotly({
  columns_to_select <- ifelse(input$Sarea_choice == "Lao",     "district_eng_preload","commune_eng_preload")
  xlab <- ifelse(input$Sarea_choice == "Lao", "District","Commune")
  pattern <- paste0("d2_132.",input$Crop_choice)
  Area <- All %>% 
    filter(S_Area == input$Sarea_choice) %>%
      select("hhid_re2", all_of(columns_to_select), matches(input$Crop_choice))
  Area <- Area[!is.na(Area[,5]),]
    if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "No" | Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Norm" ){}else{
      if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Cons"){
        Area <- Area[is.na(Area[,10]) | Area[,10] == 0,] 
         }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Sell"){
          Area <- Area[Area[,10] > 0 & !is.na(Area[,10]),]
           }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Prod"){
            Area <- Area[Area[,14] > 0 & !is.na(Area[,14]),]
             }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "NoProd"){
              Area <- Area[is.na(Area[,14]) | Area[,14] == 0,]
           }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "R"){
            Area <- Area[Area$hhid_re2 %in% Rid,] 
            }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "RnV"){
             Area <- Area[Area$hhid_re2 %in% RnVid,]
             }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "V"){
              Area <- Area[Area$hhid_re2 %in% Vid,]
              }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "VnR"){
               Area <- Area[Area$hhid_re2 %in% RnVid & Area[,5] > 0,]
              }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "DR"){
               Area <- Area[Area$hhid_re2 %in% DRid & Area[,5] > 0,]
               }else{
                x <- strsplit(gsub("\"", "", Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]), ",")[[1]]
                Area <- Area[Area$hhid_re2 %in% x,]  
               }}
    Area <- Area %>% 
      select(all_of(columns_to_select), starts_with(pattern))
  ggplotly(
    ggplot(Area, aes(x = Area[,1], y = Area[,2], fill = Area[,1])) + 
    geom_boxplot() + 
    ggtitle(paste(input$Sarea_choice," - ",input$Crop_choice,"\n", input$Cropsys_choice, "\n Area (m2) - N = ", round(Cropsys$N[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice], digits = 0)))+
    theme(legend.position='none', plot.title = element_text(size = 10))+
    ylab("Area (m2)")+
    xlab(xlab)+
    scale_fill_viridis_d()
  )
})
```

# Production, selling and additionnal {data-navmenu="Cropping systems"}

## Row 1 {data-height=300}

### **Production and selling**
**`r renderText({Cropsys$PerCentSellers[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]*100})`%** of households (% of N crop) are selling **`r renderText({input$Crop_choice})`** (Form = **`r renderText({Cropsys$MFormWhenSold[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]})`** - **`r renderText({Cropsys$PerCentMFormWhenSold[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]})`**)
```{r}
renderTable({
  Prod <- as.data.frame(t(Cropsys[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice,c(15,22:23,25:26)]))
  colnames(Prod) <- "Average"
  Prod <- Prod %>% add_column("Production & selling" = rownames(Prod), .before = "Average")
print(Prod)
})
```

### **Perception of cultivation requirements**
**`r renderText({Cropsys$"Obs-Crops requiring more water than others"[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]*100})`**% of households indicated that this Crops required more water than others\
**`r renderText({Cropsys$"Obs-Crops requiring heavy fertilization to thrive"[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]*100})`**% indicated it was requiring heavy fertilization to thrive\
**`r renderText({Cropsys$"Obs-Crops requiring heavy use of pesticides to thrive"[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]*100})`**% indicated it was requiring heavy use of pesticides to thrive

## Row 2 {data-height= 700}

### **Yield distribution**
```{r}
renderPlotly({
  columns_to_select <- ifelse(input$Sarea_choice == "Lao",     "district_eng_preload","commune_eng_preload")
  xlab <- ifelse(input$Sarea_choice == "Lao", "District","Commune")
  pattern <- paste0("d2_ha135.",input$Crop_choice)
  Area <- All %>% 
    filter(S_Area == input$Sarea_choice) %>%
      select("hhid_re2", all_of(columns_to_select), matches(input$Crop_choice))
  Area <- Area[!is.na(Area[,5]),]
    if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "No" | Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Norm" ){}else{
      if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Cons"){
        Area <- Area[is.na(Area[,10]) | Area[,10] == 0,] 
         }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Sell"){
          Area <- Area[Area[,10] > 0 & !is.na(Area[,10]),]
           }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Prod"){
            Area <- Area[Area[,14] > 0 & !is.na(Area[,14]),]
             }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "NoProd"){
              Area <- Area[is.na(Area[,14]) | Area[,14] == 0,]
           }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "R"){
            Area <- Area[Area$hhid_re2 %in% Rid,] 
            }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "RnV"){
             Area <- Area[Area$hhid_re2 %in% RnVid,]
             }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "V"){
              Area <- Area[Area$hhid_re2 %in% Vid,]
              }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "VnR"){
               Area <- Area[Area$hhid_re2 %in% RnVid & Area[,5] > 0,]
              }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "DR"){
               Area <- Area[Area$hhid_re2 %in% DRid & Area[,5] > 0,]
               }else{
                x <- strsplit(gsub("\"", "", Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]), ",")[[1]]
                Area <- Area[Area$hhid_re2 %in% x,]  
               }}
    Area <- Area %>% 
      select(all_of(columns_to_select), starts_with(pattern))
  ggplotly(
    ggplot(Area, aes(x = Area[,1], y = Area[,2], fill = Area[,1])) + 
    geom_boxplot() + 
    ggtitle(paste(input$Sarea_choice," - ",input$Crop_choice,"\n", input$Cropsys_choice, "\n Yield distribution - N = ", round(Cropsys$N[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice], digits = 0)))+
    theme(legend.position='none', plot.title = element_text(size = 10))+
    ylab("Yield (kg/ha)")+
    xlab(xlab)+
    scale_fill_viridis_d()
  )
})
```

### **Gross product/ha distribution**
```{r}
renderPlotly({
  columns_to_select <- ifelse(input$Sarea_choice == "Lao",     "district_eng_preload","commune_eng_preload")
  xlab <- ifelse(input$Sarea_choice == "Lao", "District","Commune")
  pattern <- paste0("Grossproductha.",input$Crop_choice)
  Area <- All %>% 
    filter(S_Area == input$Sarea_choice) %>%
      select("hhid_re2", all_of(columns_to_select), matches(input$Crop_choice))
  Area <- Area[!is.na(Area[,5]),]
    if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "No" | Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Norm" ){}else{
      if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Cons"){
        Area <- Area[is.na(Area[,10]) | Area[,10] == 0,] 
         }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Sell"){
          Area <- Area[Area[,10] > 0 & !is.na(Area[,10]),]
           }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "Prod"){
            Area <- Area[Area[,14] > 0 & !is.na(Area[,14]),]
             }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "NoProd"){
              Area <- Area[is.na(Area[,14]) | Area[,14] == 0,]
           }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "R"){
            Area <- Area[Area$hhid_re2 %in% Rid,] 
            }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "RnV"){
             Area <- Area[Area$hhid_re2 %in% RnVid,]
             }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "V"){
              Area <- Area[Area$hhid_re2 %in% Vid,]
              }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "VnR"){
               Area <- Area[Area$hhid_re2 %in% RnVid & Area[,5] > 0,]
              }else if(Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice] == "DR"){
               Area <- Area[Area$hhid_re2 %in% DRid & Area[,5] > 0,]
               }else{
                x <- strsplit(gsub("\"", "", Cropsys$Process[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice]), ",")[[1]]
                Area <- Area[Area$hhid_re2 %in% x,]  
               }}
    Area <- Area %>% 
      select(all_of(columns_to_select), starts_with(pattern))
  ggplotly(
    ggplot(Area, aes(x = Area[,1], y = Area[,2], fill = Area[,1])) + 
    geom_boxplot() + 
    ggtitle(paste(input$Sarea_choice," - ",input$Crop_choice,"\n", input$Cropsys_choice, "\n Gross product ($/ha) - N = ", round(Cropsys$N[Cropsys$Sarea == input$Sarea_choice & Cropsys$Crop == input$Crop_choice & Cropsys$Cropsys == input$Cropsys_choice], digits = 0)))+
    theme(legend.position='none', plot.title = element_text(size = 10))+
    ylab("$/ha")+
    xlab(xlab)+
    scale_fill_viridis_d()
  )
})
```

# AE characteristics {data-navmenu="Cropping systems"}

```{r}
renderTable({
  AEchar <- as.data.frame(Cropsyssum[Cropsyssum$Sarea == input$Sarea_choice,])
print(AEchar)
})
```


# Raising {data-navmenu="Animals"}

## Row 1 {data-height=400}

### **General**

N Study area = **`r renderText({round(sum(All$SW_Weight[All$S_Area == input$Sarea_choice]), digits = 0)})`** / N Animal = **`r renderText({AnimalDesc$N[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]})`**\
**`r renderText({AnimalDesc$PerCentofHouseholds[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** of households raise this animal specie (% of N Study area) \
Average number of adults = **`r renderText({round(AnimalDesc$NbHeadAdult[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice], digits = 2)})`**\
Number of breeds grown: **`r renderText({round(AnimalDesc$NbBreeds[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice], digits = 2)})`**\
% of breeds raised that are local: **`r renderText({AnimalDesc$LocalBreedPerCent[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%**\
**`r renderText({AnimalDesc$CrossingBreedPerCent[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** of households cross local breeds with other kind of breeds for this animal specie

### **Raising system**
<span style="color:red; font-style:italic">For pigs and chicken only:</span>\
```{r}
poultry <- c("Duck or/and Muscovy","Chicken","Other poultry","Goose")
renderTable({
  if(input$Animal_choice == "Pig"){
  Raisys <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,117:120]))
  colnames(Raisys) <- "Households (% of N Animal)"
  rownames(Raisys) <- str_replace(rownames(Raisys), "PigRaisingSystem - ", "")
  Raisys <- Raisys %>% add_column("Raising system" = rownames(Raisys), .before = "Households (% of N Animal)")
print(Raisys)    
  } else if(input$Animal_choice %in% poultry){
   Raisys <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,122:125]))
  colnames(Raisys) <- "Households (% of N Animal)"
  rownames(Raisys) <- str_replace(rownames(Raisys), "PoultryRaisingSystem - ", "")
  Raisys <- Raisys %>% add_column("Raising system" = rownames(Raisys), .before = "Households (% of N Animal)")
print(Raisys)
  } else {}

})
```

## Row 2 {data-height=600}

### **Headcounts**

Number of head (adult): **`r renderText({AnimalDesc$NbHeadAdult[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]})`**\
<span style="color:red; font-style:italic">For cattle, buffalo, pigs, goats and sheeps only:</span>\
Number of head (young): **`r renderText({AnimalDesc$NbHeadYoung[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]})`**

<span style="color:red; font-style:italic">For cattle/buffalo, the following information are tri-annual, for other animal species it is per year:</span>
```{r}
renderTable({
  Headcount <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,c(11:14,18)]))
  colnames(Headcount) <- "Average"
  Headcount <- Headcount %>% add_column("Category" = rownames(Headcount), .before = "Average")
print(Headcount)
})
```

### **Headcount distribution**
```{r}
renderPlotly({
  a <- c("Buffalo","Cattle","Pig","Goat","Sheep","Horse","Rabbit","Chicken","Duck or/and Muscovy","Goose","Other cattle","Other poultry")
  b <- c("e3_1","e3_3","e3_5","e3_7","e3_9","e3_11","e3_12","e3_13","e3_14","e3_16","e3_98","e3_99")
  Colnam <- as.data.frame(cbind(a,b))
   columns_to_select <- ifelse(input$Sarea_choice == "Lao",     "district_eng_preload","commune_eng_preload")
  xlab <- ifelse(input$Sarea_choice == "Lao", "District","Commune")
  Headcount <- All %>% 
    filter(S_Area == input$Sarea_choice) %>%
      select(all_of(columns_to_select), all_of(Colnam[Colnam$a == input$Animal_choice,2]))
  ggplotly(
    ggplot(Headcount, aes(x = Headcount[,1], y = Headcount[,2], fill = Headcount[,1])) + 
    geom_boxplot() + 
    ggtitle(paste(input$Sarea_choice," - ",input$Animal_choice,"\n Nb of head (Adult) - N = ", round(AnimalDesc$N[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice], digits = 0)))+
    theme(legend.position='none', plot.title = element_text(size = 12))+
    ylab("Nb of head (Adult)")+
    xlab(xlab)+
    scale_fill_viridis_d()
  )
})
```


# Feeding {data-navmenu="Animals"}

### **Animals location**
<span style="color:red; font-style:italic">For Cattle, Buffalo, Pigs and Poultry only:</span>\
- **`r renderText({AnimalDesc$DrySeasonGrazing[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** of households (% of N animal) put different breeds to graze together during dry season\
- **`r renderText({AnimalDesc$WetSeasonGrazing[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** of households (% of N animal) put different breeds to graze together during rainy season

```{r}
renderTable({
  DrD <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,44:48]))
  DrN <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,49:53]))
  WtD <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,67:71]))
  WtN <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,72:76]))
  Tot <- cbind(DrD,DrN,WtD,WtN)
  rownames(Tot) <- str_replace(rownames(Tot), "Dry season day - ", "")
  colnames(Tot) <- c("Dry season - Day","Dry season - Night","Wet season - Day","Wet season - Night")
  Tot <- Tot %>% add_column("Places" = rownames(Tot), .before = "Dry season - Day")
print(Tot)
})
```


### **Animals feed**
<span style="color:red; font-style:italic">For Cattle, Buffalo, Pigs and Poultry only:</span>\
- Use of concentrate from the farm (% of N Animal): **`r renderText({AnimalDesc$'ConcentrateUse - From farm'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%**\
- Use of concentrate from the market: **`r renderText({AnimalDesc$'ConcentrateUse - From market'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%**


```{r}
renderTable({
  DrFe <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,c(55:65,121,66)]))
  WtFe <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,78:90]))
  Tot <- cbind(DrFe,WtFe)
  rownames(Tot) <- str_replace(rownames(Tot), "Dry season day - ", "")
  colnames(Tot) <- c("Dry season feeding","Wet season feeding")
  Tot <- Tot %>% add_column("Feed" = rownames(Tot), .before = "Dry season feeding")
  Tot <- Tot %>%
    filter(!is.na(`Dry season feeding`) & !is.na(`Wet season feeding`), rowSums(Tot[,2:3]) != 0)
print(Tot)
})
```


# Care {data-navmenu="Animals"}

### **Parasites & diseases**
<span style="color:red; font-style:italic">For Cattle, Buffalo, Pigs and Poultry only:</span>

Households facing problems with animal diseases (% of N Animal): **`r renderText({AnimalDesc$Diseases[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%**

Household facing problems with animal parasites (% of N Animal):
```{r}
renderTable({
  Para <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,c(93:95)]))
  rownames(Para) <- str_replace(rownames(Para), "Parasites - ", "")
  colnames(Para) <- "households concerned (% of N Animal)"
  Para <- Para %>% add_column("Parasite kind" = rownames(Para), .before = "households concerned (% of N Animal)")
print(Para)
})
```


### **Care and antibiotics**
<span style="color:red; font-style:italic">For Cattle, Buffalo, Pigs and Poultry only:</span>\

Treatment used for animals care (% of N Animal):

- **`r renderText({AnimalDesc$'Care - Traditional treatment'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** of households are using traditional treatments
- **`r renderText({AnimalDesc$'Care - Chemicals'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** of households are using chemicals

Reasons for using a traditionnal or chemical treatment (% of N Animal):

- **`r renderText({AnimalDesc$'CareReasonYes - Better for environment/ AE'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** used a treatment because they thought it is better for environment
- **`r renderText({AnimalDesc$'CareReasonYes - Human health'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** used a treatment because they thought it is better for human health
- **`r renderText({AnimalDesc$'CareReasonYes - Treatment / prevention'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** used a treatment to solve existing issues or prevent future issues

Reasons for not using a traditionnal or chemical treatment (% of N Animal):

- **`r renderText({AnimalDesc$'CareReasonNo - Not available on the market'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** did not use a treatment because it was not available on the market
- **`r renderText({AnimalDesc$'CareReasonNo - Too expensive'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** did not use a treatment because it was too expensive
- **`r renderText({AnimalDesc$'CareReasonNo - No need, not severe disease'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** did not use a treatment because there was no severe disease
- **`r renderText({AnimalDesc$'CareReasonNo - Too difficult to handle animal or no VT service'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** did not use a treatment because there was no VT service or it was too difficult to handle animal

Use of antibiotics (% of N Animal):

- **`r renderText({AnimalDesc$'Antibiotics - For treatment diseases only'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** used antibiotics as a treatment for diseases
- **`r renderText({AnimalDesc$'Antibiotics - For prevention of diseases only'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** used antibiotics to prevent diseases
- **`r renderText({AnimalDesc$'Antibiotics - For growth promotion'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** used antibiotics to promote animal growth

Reasons given by households who used antibiotics (% of N Animal):

- **`r renderText({AnimalDesc$'AntibioticsReasonYes - Better for environment/ AE'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** used antibiotics for positive effect on environment/AE
- **`r renderText({AnimalDesc$'AntibioticsReasonYes - Human health'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** used antibiotics for positive effect on human health
- **`r renderText({AnimalDesc$'AntibioticsReasonYes - Treatment / prevention'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** used antibiotics to solve existing issues or prevent future issues

Reasons given by households who did not use antibiotics (% of N Animal):

- **`r renderText({AnimalDesc$'AntibioticsReasonNo - Not available on the market'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** did not use antibiotics as it was not available on the market
- **`r renderText({AnimalDesc$'AntibioticsReasonNo - Too expensive'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** did not use antibiotics as it was too expensive
- **`r renderText({AnimalDesc$'AntibioticsReasonNo - Already include in the feed'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** did not use antibiotics as it was already included in the feed
- **`r renderText({AnimalDesc$'AntibioticsReasonNo - No need, not severe disease'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** did not use antibiotics as there was no severe disease
- **`r renderText({AnimalDesc$'AntibioticsReasonNo - Too difficult to handle animal or no VT service'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** did not use antibiotics as there was no VT service or it was too difficult to handle animals

# Production {data-navmenu="Animals"}

## Row 1 {data-height=500}

### **Production details**
**`r renderText({AnimalDesc$HouseholdsSellingPerCent[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%** of households (% of N Animal) sold animals during the past year (or 3 last years for cattle/buffalo) 

<span style="color:red; font-style:italic">For cattle/buffalo, the following information are tri-annual, for other animal species it is per year:</span>
```{r}
renderTable({
  Prod <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,c(14:15,17,16,18:20)]))
  rownames(Prod)[7] <- "Gross product ($/year - 3years for cattle/buffalo)"
  colnames(Prod) <- "Values"
  Prod <- Prod %>% 
    add_column("Characteristics" = rownames(Prod), .before = "Values")
print(Prod)
})
```

### **Buying price distribution**
```{r}
renderPlotly({
   columns_to_select <- ifelse(input$Sarea_choice == "Lao",     "district_eng_preload","commune_eng_preload")
  xlab <- ifelse(input$Sarea_choice == "Lao", "District","Commune")
  pattern <- paste0("e5_51.",input$Animal_choice)
  BuyPrice <- All %>% 
    filter(S_Area == input$Sarea_choice) %>%
      select(all_of(columns_to_select), starts_with(pattern))
  ggplotly(
    ggplot(BuyPrice, aes(x = BuyPrice[,1], y = BuyPrice[,2], fill = BuyPrice[,1])) +     geom_boxplot() + 
    ggtitle(paste(input$Sarea_choice," - ",input$Animal_choice,"\n Buying price ($ per head or kg) - N = ", round(AnimalDesc$N[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice], digits = 0)))+
    theme(legend.position='none', plot.title = element_text(size = 12))+
    ylab("Buying price ($ per head or kg)")+
    xlab(xlab)+
    scale_fill_viridis_d()
  )
})
```

## Row 2 {data-height=500}

### **Amount sold distribution (nb of head/year - /3 years for cattle/buffalo)**
```{r}
renderPlotly({
   columns_to_select <- ifelse(input$Sarea_choice == "Lao",     "district_eng_preload","commune_eng_preload")
  xlab <- ifelse(input$Sarea_choice == "Lao", "District","Commune")
  pattern <- paste0("e5_4.",input$Animal_choice)
  BuyPrice <- All %>% 
    filter(S_Area == input$Sarea_choice) %>%
      select(all_of(columns_to_select), starts_with(pattern))
  ggplotly(
    ggplot(BuyPrice, aes(x = BuyPrice[,1], y = BuyPrice[,2], fill = BuyPrice[,1])) +     geom_boxplot() + 
    ggtitle(paste(input$Sarea_choice," - ",input$Animal_choice,"\n Amount sold (number of head) - N = ", round(AnimalDesc$N[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice], digits = 0)))+
    theme(legend.position='none', plot.title = element_text(size = 12))+
    ylab("Amount sold (number of head)")+
    xlab(xlab)+
    scale_fill_viridis_d()
  )
})
```

### **Gross product distribution ($)**
```{r}
renderPlotly({
   columns_to_select <- ifelse(input$Sarea_choice == "Lao",     "district_eng_preload","commune_eng_preload")
  xlab <- ifelse(input$Sarea_choice == "Lao", "District","Commune")
  pattern <- paste0("e5_43.",input$Animal_choice)
  BuyPrice <- All %>% 
    filter(S_Area == input$Sarea_choice) %>%
      select(all_of(columns_to_select), starts_with(pattern))
  ggplotly(
    ggplot(BuyPrice, aes(x = BuyPrice[,1], y = BuyPrice[,2], fill = BuyPrice[,1])) +     geom_boxplot() + 
    ggtitle(paste(input$Sarea_choice," - ",input$Animal_choice,"\n Gross product ($) - N = ", round(AnimalDesc$N[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice], digits = 0)))+
    theme(legend.position='none', plot.title = element_text(size = 12))+
    ylab("Gross product ($)")+
    xlab(xlab)+
    scale_fill_viridis_d()
  )
})
```


# Outlet/Buyer {data-navmenu="Animals"}

## Row 1 {data-height=500}

### **Buyers/Outlets** (For all parts on this page values are % of N animal, no % of sellers)
```{r}
renderTable({
  Buyer <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,c(21:28)]))
  rownames(Buyer) <- str_replace(rownames(Buyer), "Main outlet - ", "")
  colnames(Buyer) <- "households concerned (% of N Animal)"
  Buyer <- Buyer %>% 
    add_column("Outlet-Buyer" = rownames(Buyer), .before = "households concerned (% of N Animal)") %>% filter(`households concerned (% of N Animal)` > 0)
print(Buyer)
})
```

### **Provided by Buyer/Outlet**
```{r}
renderTable({
  ProvBuy <- as.data.frame(t(AnimalDesc[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice,c(33:39)]))
  rownames(ProvBuy) <- str_replace(rownames(ProvBuy), "ProvidedBuyer", "")
  colnames(ProvBuy) <- "households concerned (% of N Animal)"
  ProvBuy <- ProvBuy %>% 
    add_column("Provided by Outlet/Buyer" = rownames(ProvBuy), .before = "households concerned (% of N Animal)") %>% filter(`households concerned (% of N Animal)` > 0)
print(ProvBuy)
})
```

## Row 2 {data-height=500}

### **% of production sold to the main outlet:**
- 0-25%: **`r renderText({AnimalDesc$'ShareSoldMainOutlet - Less than 25%'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%**
- 25-50%: **`r renderText({AnimalDesc$'ShareSoldMainOutlet - 25-50%'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%**
- 50-75%: **`r renderText({AnimalDesc$'ShareSoldMainOutlet - 50-75%'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%**
- 75-100% :**`r renderText({AnimalDesc$'ShareSoldMainOutlet - Over 75%'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%**

### **Kind of contracts**
- Formal contract: **`r renderText({AnimalDesc$'ContractKind - Formal contract'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%**
- Informal contract: **`r renderText({AnimalDesc$'ContractKind - Informal contract'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%**
- No contract/no prior arrangements: **`r renderText({AnimalDesc$'ContractKind - No contract/ no prior arrangements'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%**
- Spot relations:**`r renderText({AnimalDesc$'ContractKind - Spot relations'[AnimalDesc$S_Area == input$Sarea_choice & AnimalDesc$specie == input$Animal_choice]*100})`%**

# Overview {data-navmenu="Raising systems"}
```{r}
output$image2 <- renderImage({
  switch(input$Sarea_choice,
         "Cambodia" = list(src = "AnimSysOverview_Camb.jpg", width = "90%"),
         "Lao" = list(src = "AnimSysOverview_Laos.jpg", width = "90%"),
         "Son La province" = list(src = "AnimSysOverview_SL.jpg", width = "90%"),
         "Dien Bien province" = list(src = "AnimSysOverview_DB.jpg", width = "90%"))
}, deleteFile = FALSE)

imageOutput("image2")
```


